The mass relations between supermassive black holes and their host galaxies at $1< z<2$ with \hst-WFC3

### 2019-07-31 manuscript/manuscript.tex
Before move to new Mac

\begin{figure*}
\centering
\begin{tabular}{c c}
{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_style1.pdf}}&
{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_style0.pdf}}\\
\end{tabular}
\caption{\label{fig:MM-vz} 
 {\it Left}: Offset in  $\log($\mbh$)$ (vs. \smass) as a function of redshift. The orange band is the intrinsic scatter of local linear relation. The red line and gray band are the best-fit and $1\sigma$ offset fitting by Equation~\ref{eq:offset} using our 32 high-$z$ AGNs, with slope value $\gamma  = 0.78 \pm 0.26$.
 {\it Right}: \mbh/\smass\ as a function of redshift. 
We use green open circles to show the expected shifting of the median value of the $\Delta \log$\mbh\ before and after consider the selection effect using framework by \citet{Schulze2011} in Section~\ref{sec:sf_framework}.}
\end{figure*}

@@

%Then, we calculate the average B/T
%ratio at different \sersic\ index to construct a relation for our
%use, as shown in Figure~\ref{fig:BT-n_relation}. Taking this
%relation, we estimate the B/T of our AGN sample using the \sersic\
%index as proxy and infer their \smass$_{\rm, bulge}$ from the total
%stellar mass.
%We can now compare this \smass$_{\rm, bulge}$ to that
%of the black hole \mbh.
As expected, we find a stronger offset of
$0.74\pm0.12$~dex in \mbh/\smass$_{\rm, bulge}$ with respect to the
local relation, which corresponds to an evolutionary trend with
$\gamma = 1.86\pm0.30$. Since selection effects are independent of B/T in
our framework we can apply our a-priori estimate of the selection
effect correction by removing $0.21$~dex, leaving a significant offset
of $0.53\pm0.12$. {\bf We show the histogram of $\gamma$ inferred by
the Monte Carlo approach in Figure~\ref{fig:gamma_hist}. Same as
Figure~\ref{fig:MM-vz}, we illustrate the offset between bulge and BH
as a function of redshift, in Figure~\ref{fig:MM_bulge-vz}.}

@@

\begin{figure}
\centering
{
\includegraphics[width=0.5\textwidth]{fig/gamma_hist.pdf}
}
\caption{\label{fig:gamma_hist} 
Illustration of the $\gamma$ distribution from the $10,000$ time realization.
}
\end{figure}

>>>>

\begin{figure*}
\centering
\begin{tabular}{c c}
{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_style1.pdf}}&
{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_style0.pdf}}\\
\end{tabular}
\caption{\label{fig:MM-vz} 
 {\it Left}: Offset in  $\log($\mbh$)$ (vs. \smass) as a function of redshift. The orange band is the intrinsic scatter of local linear relation. The red line and gray band are the best-fit and $1\sigma$ offset fitting by Equation~\ref{eq:offset} using our 32 high-$z$ AGNs, with slope value $\gamma  = 0.78 \pm 0.26$.\\
 {\it Right}: \mbh/\smass\ as a function of redshift. 
We use green open circles to show the expected shifting of the median value of the $\Delta \log$\mbh\ before and after consider the selection effect using framework by \citet{Schulze2011} in Section~\ref{sec:sf_framework}.}
\end{figure*}

@@

%Then, we calculate the average B/T
%ratio at different \sersic\ index to construct a relation for our
%use, as shown in Figure~\ref{fig:BT-n_relation}. Taking this
%relation, we estimate the B/T of our AGN sample using the \sersic\
%index as proxy and infer their \smass$_{\rm, bulge}$ from the total
%stellar mass.
%We can now compare this \smass$_{\rm, bulge}$ to that
%of the black hole \mbh.
As expected, we find a stronger offset of
$0.74\pm0.12$~dex in \mbh/\smass$_{\rm, bulge}$ with respect to the
local relation, which corresponds to an evolutionary trend with
$\gamma = 1.86\pm0.30$. Since selection effects are independent of B/T in
our framework we can apply our a-priori estimate of the selection
effect correction by removing $0.21$~dex, leaving a significant offset
of $0.53\pm0.12$. {\bf We show the histogram of  \mbh/\smass\ and $\gamma$ inferred by
the Monte Carlo approach in Figure~\ref{fig:gamma_hist}. Same as
Figure~\ref{fig:MM-vz}, we illustrate the offset between bulge and BH
as a function of redshift, in Figure~\ref{fig:MM_bulge-vz}.}

@@

\begin{figure*}
\centering
\begin{tabular}{c c}
{\includegraphics[height=0.39\textwidth]{fig/realizations_M_BH_M_star.pdf}}&
{\includegraphics[height=0.39\textwidth]{fig/gamma_hist.pdf}}\\
\end{tabular}
\caption{\label{fig:gamma_hist} 
Illustration of the distribution from the $10,000$ time realization. {\it Left}: \mbh/\smass\ distribution for 32 high-$z$ sample, compared to the local one. {\it Right}: $\gamma$ distribution.
}
\end{figure*}
